---
title: "RepData-PeeAssessment2"
author: "Dawit Gebremichael"
date: "February 21, 2015"
output: html_document
---

<h1>Synopsis</h1>

 This asssignment attempt to explore the NOAA Storm Database and answer some basic questions about severe weather events from  the U.S. National Oceanic and Atmospheric Administration's storm database. The program loads the data, which is csv format. Then it looks into 

<h2>Data processing</h2>

The following shows that all data is loaded and displayed partially.

```{r}

library(plyr)
if(!exists("data")){
    data <- read.csv(file="repdata-data-StormData.csv",head=T,stringsAsFactors=FALSE, cache = TRUE )
}
head(data)
    
```

Below, it aggregates all fatalities and ilter by the most fatalities

```{r, echo=FALSE}
# fetalities <- aggregate(FATALITIES ~ EVTYPE, data = data, FUN=sum, na.rm=TRUE) # ||  data[data$FATALITIES > 0, ] 
# #sort the data in descending order
# fetalities <- fetalities[order(fetalities$FATALITIES, decreasing = TRUE), ]
# #display the portion of the data
# head(fetalities)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
